Spatial phylogenetics of Japanese ferns: Patterns, processes, and implications for conservation

### 2023-03-28 ms/manuscript.Rmd
Update MS
Update ms use standard fig dpi throughout

Joel H. Nitta, #601 Bioscience Bldg, The University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa, Chiba 277-0882, Japan

@@

# Format biodiv_ferns_spatial data for plotting
biodiv_ferns_spatial <-
  biodiv_ferns_spatial %>%
  # Set order of factor levels for plotting
  mutate(
    endem_type = factor(
      endem_type,
      levels = c("neo", "paleo", "not significant", "mixed", "super")),
    # can ignore warning about unknown levels, since they don't exist in all
    # variables but that's OK
    across(
      contains("signif"),
      ~fct_relevel(.x,
      "< 0.01",  "< 0.025", "not significant", "> 0.975", "> 0.99")
    )
  ) %>%
  st_transform(4612)
```

@@

```{r japan-map-save, eval = params$doc_type == "doc"}
# Save plot if rendering to doc
ggsave(
  result_file(figure("japan-map"), "pdf"),
  japan_map_plot, width = 5, height = 5, units = "in")
```

@@

```{r raw-diversity-save, eval = params$doc_type == "doc"}
# Save plot if rendering to doc
ggsave(
  result_file(figure("raw-diversity"), "pdf"),
  width = 7.25, height = 3.4, units = "in", raw_diversity_plot)
```

@@

```{r rand-diversity-save, eval = params$doc_type == "doc"}
# Save plot if rendering to doc
ggsave(
  result_file(figure("rand-diversity"), "pdf"),
  rand_diversity_plot, width = 7.25, height = 8, units = "in")
```

@@

```{r coeff-save, eval = params$doc_type == "doc"}
# Save plot if rendering to doc
ggsave(
  result_file(figure("coeff"), "pdf"),
  coeff_plot, width = 7.25, height = 5, units = "in")
```

@@

```{r modelfit-save, eval = params$doc_type == "doc"}
# Save plot if rendering to doc
ggsave(
  result_file(figure("modelfit"), "pdf"),
  modelfit_plot, width = 7.25, height = 5, units = "in")
```

@@

```{r endemism-save, eval = params$doc_type == "doc"}
# Save plot if rendering to doc
ggsave(
  result_file(figure("endemism"), "pdf"),
  endemism_plot, width = 5, height = 5, units = "in")
```

@@

```{r bioregions-save, eval = params$doc_type == "doc"}
# Save plot if rendering to doc
ggsave(
  result_file(figure("bioregions"), "pdf"),
  bioregions_plot, width = 7.25, height = 4.3, units = "in")
```

@@

```{r div-by-tax-region-save, eval = params$doc_type == "doc"}
# Save plot if rendering to doc
ggsave(
  result_file(figure("div-by-tax-region"), "pdf"),
  div_by_tax_region_plot, width = 7.25, height = 7, units = "in")
```

@@

```{r conserv-status-save, eval = params$doc_type == "doc"}
# Save plot if rendering to doc
ggsave(
  result_file(figure("conserv-status"), "pdf"),
  conserv_status_plot, width = 7.25, height = 4, units = "in")
```

>>>>

Joel H. Nitta, #601 Bioscience Bldg., The University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa, Chiba 277-0882, Japan

@@

# Format biodiv_ferns_spatial data for plotting
biodiv_ferns_spatial <-
  biodiv_ferns_spatial %>%
  # Set order of factor levels for plotting
  mutate(
    endem_type = factor(
      endem_type,
      levels = c("neo", "paleo", "not significant", "mixed", "super")),
    # can ignore warning about unknown levels, since they don't exist in all
    # variables but that's OK
    across(
      contains("signif"),
      ~fct_relevel(.x,
      "< 0.01",  "< 0.025", "not significant", "> 0.975", "> 0.99")
    )
  ) %>%
  st_transform(4612)

fig_dpi <- 600
```

@@

```{r japan-map-save, eval = params$doc_type == "doc"}
# Save plot if rendering to doc
ggsave(
  result_file(figure("japan-map"), "png"),
  japan_map_plot, width = 5, height = 5, units = "in", dpi = fig_dpi)
```

@@

```{r raw-diversity-save, eval = params$doc_type == "doc"}
# Save plot if rendering to doc
ggsave(
  result_file(figure("raw-diversity"), "png"),
  width = 7.25, height = 3.4, units = "in", raw_diversity_plot, dpi = fig_dpi)
```

@@

```{r rand-diversity-save, eval = params$doc_type == "doc"}
# Save plot if rendering to doc
ggsave(
  result_file(figure("rand-diversity"), "png"),
  rand_diversity_plot, width = 7.25, height = 8, units = "in", dpi = fig_dpi)
```

@@

```{r coeff-save, eval = params$doc_type == "doc"}
# Save plot if rendering to doc
ggsave(
  result_file(figure("coeff"), "png"),
  coeff_plot, width = 7.25, height = 5, units = "in", dpi = fig_dpi)
```

@@

```{r modelfit-save, eval = params$doc_type == "doc"}
# Save plot if rendering to doc
ggsave(
  result_file(figure("modelfit"), "png"),
  modelfit_plot, width = 7.25, height = 5, units = "in", dpi = fig_dpi)
```

@@

```{r endemism-save, eval = params$doc_type == "doc"}
# Save plot if rendering to doc
ggsave(
  result_file(figure("endemism"), "png"),
  endemism_plot, width = 5, height = 5, units = "in", dpi = fig_dpi)
```

@@

```{r bioregions-save, eval = params$doc_type == "doc"}
# Save plot if rendering to doc
ggsave(
  result_file(figure("bioregions"), "png"),
  bioregions_plot, width = 7.25, height = 4.3, units = "in", dpi = fig_dpi)
```

@@

```{r div-by-tax-region-save, eval = params$doc_type == "doc"}
# Save plot if rendering to doc
ggsave(
  result_file(figure("div-by-tax-region"), "png"),
  div_by_tax_region_plot, width = 7.25, height = 7, units = "in", dpi = fig_dpi)
```

@@

```{r conserv-status-save, eval = params$doc_type == "doc"}
# Save plot if rendering to doc
ggsave(
  result_file(figure("conserv-status"), "png"),
  conserv_status_plot, width = 7.25, height = 4, units = "in", dpi = fig_dpi)
```
